Research on The Impact of Past Behaviour Normality on Regret

### 2024-02-14 outputs/paper/paper.qmd
result section updated

# Results
## Experiment 1

@@

>>>>

# Results {#sec-res}
=======
## Experiment 1

### Regret

From what we learned before, we expected that participants would believe Mr. Jones, who rarely picks up hitchhikers, would feel more regret than Mr. Smith, who does so often. It turns out, most participants did think Mr. Jones would feel worse (315 responses, or 92%) compared to Mr. Smith (27 responses, or 8%), as shown in the @fig-experiment1bar.

### Social norms

Taking our research a step further, we hypothesized that participants would see Mr. Jones's behavior (not picking up hitchhikers) as more typical or normal, and Mr. Smith's behavior (picking up hitchhikers) as less typical and more likely to be judged by others. This was indeed what we found: most people thought Mr. Jones's actions were more common (326 responses, or 95%) and Mr. Smith's actions were more likely to face social criticism (310 responses, or 91%), as shown in the tbl-experiment1.

@@

### Regret

We had a hunch that participants would feel Mr. White, who had an accident on an unusual route home, would regret his decision more than Mr. Adams, who had his accident on his regular drive home. And it turns out, that's exactly what most participants thought: 277 of them (81%) associated a higher level of regret with Mr. White's unusual decision, while only 65 of them (19%) thought Mr. Adams would feel more regret, as shown in the @fig-experiment2bar.

Thus, our study confirmed our guess: Mr. White's one-off decision led to more regret among our participants than Mr. Adams's everyday routine, suggesting that when bad things happen on a path less traveled, they hit us harder.
